On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-19 MS.tex
Abstract modification to hilight the need of further empirical studies for underrepresented trait size classes combinations

\item Results were consistent with predictions. Specific leaf area was correlated with relative growth rate (RGR) in seedlings but not in adult plants. Correlations of RGR with wood density and assimilation rate were not affected by stage. Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively. Yet, despite a sizeable literature on traits and growth, coverage was still limited for wood density, seed mass, maximum height and assimilation rate. Additional studies are needed for some trait-growth-stage relationships.

>>>>

\item Results were consistent with predictions. Specific leaf area was correlated with relative growth rate (RGR) in seedlings but not in adult plants. Correlations of RGR with wood density and assimilation rate were not affected by stage. Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively. Despite a sizeable literature on traits and growth, coverage was still limited for wood density, seed mass, maximum height and assimilation rate. There is still scope for strengthening our understanding of correlations between traits and growth through adding further empirical studies for  traits and size-classes underrepresented in the literature.
